SOL Filamentary transport: update from joint AUG-TCV MST1 experiment

### 2018-01-25 Meetings/25ITPADivSOL/vianello_25itpadivsol.tex
Update to TeX and pdf for ITPA presentation

@@

    \item<2|only@2> Different behavior of ELM during the fueling
      ramp. ELM size and frequency changes strongly without the
      cryopump or during extreme fueling case
    \item<3|only@3> Profiles
    \item<4|only@4> Without the cryopumps, we reached flatter
         profiles with comparable inter-ELM resolved blob-size. This
         indicates strong neutral pressure effects in determining
         upstream profiles
    \item<5|only@5> Increasing the fueling and correspondingly the
      divertor neutral pressure move towards a situation similar to
      \# 34276 without the cryopump
      \end{itemize}
  \end{column}
\end{columns}
\end{frame}

>>>>

  \centering{\includegraphics<3>[height=0.75\textheight]{../../Experiments/AUG/analysis/pdfbox/UpstreamDivertorProfiles34276_34278_34281}}

@@

    \item<2|only@2> Different behavior of ELM during the fueling
      ramp. ELM size and frequency changes strongly without the
      cryopump or during extreme fueling case
    \item<3|only@3> The profiles for shot \# 34278 with the cryopum
      and lower fueling remains more steep in all the three timing
      wind and the plasma is still attached. Interestingly for shot \#
      34281 with the cryopumps and higher fueling the detachment is
      more pronounced
    \item<4|only@4> Without the cryopumps, we reached flatter
         profiles with comparable inter-ELM resolved blob-size. This
         indicates strong neutral pressure effects in determining
         upstream profiles
    \item<5|only@5> Increasing the fueling and correspondingly the
      divertor neutral pressure move towards a situation similar to
      \# 34276 without the cryopump
      \end{itemize}
  \end{column}
\end{columns}
\end{frame}
